Analysis : exp320-21 g_KCa analysis

### 2019-08-21 resistingrhythm/analysis/exp320_321.Rmd
G_KCA analysis

---
title: "Analysis : exp316-7 g_L analysis"
output: html_notebook
---

@@

# Load G_Ca
```{r, message=FALSE}
# Main exp
# -----------------------------------------------------------------------
# 15: Sustained E, with H
exp_code <- 221
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4)

results221 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

    # Load the csv
    df <- read_csv(paste(data_path, 
                         "exp", as.character(exp_code), 
                         "_stim", as.character(s_c), 
                         "_osc", as.character(o_c),
                         ".csv", sep=""))

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$g_L <- rep("1.0e-3", nrow(df))
    df$homeo <- rep("Homeostasis", nrow(df))
    df$freq <- rep(8, nrow(df))
    results221 <- rbind(results221, df)
  }
}

results221 %>%
  filter(rate_k > 0) -> results221

# ----------------------------------------------------------------------
# gL perturb exps
# H
exp_code <- 317
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results317 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

@@

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_gl", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

@@

      results317 <- rbind(results317, df)
    }
  }
}
results317 %>%
  filter(rate_k > 0) -> results317

# no H
exp_code <- 316
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_Ls <- c("0.9e-3", "0.95e-3", "1.05e-3", "1.1e-3")

results316 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_Ls){

@@

      results316 <- rbind(results316, df)
    }
  }
}
results316 %>%
  filter(rate_k > 0) -> results316

results <- rbind(
  results316,
  results317,
  results221
)

results$g_L <- factor(results$g_L, levels=c("0.9e-3", "0.95e-3", "1.0e-3", "1.05e-3", "1.1e-3"))
```

# Plot
## Individual points
```{r, fig.height=1.2, fig.width=3.5}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_point(size=.5, alpha=0.6) +
  theme_classic() +
  scale_color_viridis_d() +
  facet_grid(homeo~., scales = "free")
```

>>>>

---
title: "Analysis : exp320-21 g_KCa analysis"
output: html_notebook
---

@@

# Load G_KCa
```{r, message=FALSE}
# ----------------------------------------------------------------------
# G_KCA perturb exps
# H
exp_code <- 321
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_KCas <- c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3")

results321 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_KCas){

@@

      # Load the csv
      # exp316_stim{1}_gl{3}_osc
      df <- read_csv(paste(data_path, 
                           "exp", as.character(exp_code), 
                           "_stim", as.character(s_c), 
                           "_GKCa", as.character(g), 
                           "_osc", as.character(o_c),
                           ".csv", sep=""))

@@

      results321 <- rbind(results321, df)
    }
  }
}
results321 %>%
  filter(rate_k > 0) -> results321

# no H
exp_code <- 320
osc_codes <- c(100, 115)
osc_rates <- c(0, 1.5)
stim_codes <- c(3, 4) # 4
g_KCas <- c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3")

results320 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    for(g in g_KCas){

@@

      results320 <- rbind(results320, df)
    }
  }
}
results320 %>%
  filter(rate_k > 0) -> results320

results <- rbind(
  results320,
  results321
)

results$g_L <- factor(results$g_L, levels=c("0.1e-3", "1e-3", "15e-3", "30e-3", "45e-3", "60e-3"))
```

# Plot
## Individual points
```{r, fig.height=1.2, fig.width=3.5}
results %>% 
  ggplot(aes(x=osc_rate, y=kappa_coord, group=interaction(osc_rate, homeo), color=g_L)) +
  geom_point(size=.5, alpha=0.6) +
  theme_classic() +
  scale_color_grey() +
  facet_grid(homeo~g_L, scales = "free")
```
